---
title: "Congress Report"
author: "Alexander Harr"
date: "2/5/2017"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("knitr")
library("httr")
library("jsonlite")
library("dplyr")
base.uri <- "https://congress.api.sunlightfoundation.com/"
search.query <- "oceans" 
zip.code <- as.integer(95125)
roll.id <- "s52-2017"
options(scipen = 999)
```
#The purpose of this report is to generate a report of congressional representatives in the zip code `r zip.code`

```{r district.reps, echo = FALSE}
#Isolate data frame and flatten
end.point <- "legislators/locate"
response <- GET(paste0(base.uri, end.point), query = list(zip = zip.code))
body <- fromJSON(content(response, "text"))
df <- flatten(body$results) %>% select(first_name, last_name, state, party, phone)
#Function to produce list output
LocalRep <- function(row) {
  temp <- df[row, ]
  statement <- paste0(temp$first_name, " ", temp$last_name, " (", temp$state, "-", temp$party, "). Phone: ", temp$phone)
  return(statement)
}
```
The representatives for this district are 

* `r LocalRep(1)`

* `r LocalRep(2)`

* `r LocalRep(3)`

* `r LocalRep(4)`
```{r Congressional.bills, echo = FALSE }
end.point <- "bills/search"

query.params <- list(query = search.query, history.active = "true", order = "introduced_on", per_page = 25)

response <- GET(paste0(base.uri, end.point), query = query.params)

body <- fromJSON(content(response, "text"))

df <- flatten(body$results)

df <- df %>% select(Bill = bill_id, Introduced = introduced_on, Title = official_title, Link = urls.congress)

df$Link <- paste0("[Link](", df$Link, ")")

table <- kable(df, format = "markdown", col.names = colnames(df))
```
#Congressional Bills
The table below lists the 25 most recent bills regarding `r search.query` that are currently *being discussed by congress*. 

`r table`

```{r Voting.Issue, echo = FALSE }
end.point <- "votes"

query.params <- list(roll_id = roll.id, fields = "voters")

get.request.result <- GET(paste0(base.uri, end.point), query = query.params)
#sets the body of the content as a list
request.body.as.list <- content(get.request.result)
#then takes the list and acesses the first vector of the r.b.a.list which is another list and then
#from that list accesses the voters
voters.list <- request.body.as.list$results[[1]]$voters
#the colnames and rownames are now renamed to have no value
names(voters.list) <- NULL
#parses the list into JSON
voters.json <- toJSON(voters.list)
#Creates a data frame from voters.json by flattening it 
voters.as.data.frame <- flatten(fromJSON(voters.json, flatten=TRUE))

small.df <- voters.as.data.frame %>% select(voter.first_name, voter.last_name, voter.party, vote)

table <- kable(small.df, format = "markdown", col.names = colnames(small.df))
```
#Indivdual Votes
These votes entail the motion to Invoke Colture on the Nomination of Elisabeth DeVos to be secretary of Education, click here for more [information](https://www.govtrack.us/congress/votes/115-2017/s52). 

`r table`

```{r party, echo = FALSE}
end.point <- "votes"

roll.id <- "s52-2017"

query.params <- list(roll_id = roll.id, fields = "voters")

get.request.result <- GET(paste0(base.uri, end.point), query = query.params)
#sets the body of the content as a list
request.body.as.list <- content(get.request.result)
#then takes the list and acesses the first vector of the r.b.a.list which is another list and then
#from that list accesses the voters
voters.list <- request.body.as.list$results[[1]]$voters
#the colnames and rownames are now renamed to have no value
names(voters.list) <- NULL
#parses the list into JSON
voters.json <- toJSON(voters.list)
#Creates a data frame from voters.json by flattening it 
voters.as.data.frame <- flatten(fromJSON(voters.json, flatten=TRUE))
small.df <- voters.as.data.frame %>% select(voter.first_name, voter.last_name, voter.party, vote)

party.votes <- voters.as.data.frame %>% select(vote, voter.chamber, voter.party)

republicans <- party.votes %>% filter(voter.party == "R") %>% mutate(did.vote.yes = vote == "Yea")

democrats <- party.votes %>% filter(voter.party == "D") %>% mutate(did.vote.yes = vote == "Yea")

independents <- party.votes %>% filter(voter.party == "I") %>% mutate(did.vote.yes = vote == "Yea")

final <- data.frame(voter.party = c("R", "D", "I"),vote =  c("Yea", "Nay", "Nay"),chamber =  c("Senate", "Senate", "Senate"), total.party = 
                    c(length(republicans$did.vote.yes), length(democrats$did.vote.yes), length(independents$did.vote.yes)), stringsAsFactors = FALSE)
table <- kable(final, format = "markdown", col.names = colnames(final))
table2 <- kable(party.votes, format = "markdown", col.names = colnames(party.votes))
```
The table below details the party breakdown of the votes and what each party voted for
`r table`
The table below details the party votes and individual votes
`r table2`
